Analysis of competitive surfing tournaments with generalized Bradley-Terry likelihoods

### 2022-09-25 inst/surfing_jsa_rebuttal_minorcomments.tex

Contextual changes and clarifications

Page 2: The first reference to the ``World Championship Tour'' would
benefit from including a one-off abbreviation (WCT), which is referred
to throughout the data set.

\textcolor{blue}{Done; WSL used throughout for ``World Surf League''
  and minor rewording ensures that the phrase ``World Championship
  Tour'' does not appear}

Page 4: It is mentioned in the abstract that the analysis is performed
on data from the 2019 WSL, however a reference in the main text at the
top of Section 5 would help clarify this.

\textcolor{blue}{Done}

Page 4: The authors mention the surfer Vries---who does not appear to
be a wildcard---whose maximum likelihood strength is zero. Why is
this? My guess is that Vries has never won a competitive surfing heat
(and therefore there is no information on his true, underlying
ability), however a brief clarification here woud be useful.

\textcolor{blue}{The referee is quite right: Vries competed only twice
  in 2019, coming last (second and third) in each of his two sessions.
  Brief explanation added to he mauscript.}

Page 6 / Figure 1: I’m pleased to see the authors replace the old pie chart in Figure 1 with a dot chart
– this is a much clearer visualization of the results. On Page 6 the authors state: “Figure 1 shows the
maximum likelihood estimate for the 23 competitors’ strengths, which appears to show a wide range
from Florence at about 17.5% down to Morais at about 1%”. What exactly do the quantities 17.5%
and 1% refer to/how are they computed? A quick clarification of these quantities would help explain
the practical implications of the findings.
Page 7/Figure 2: The authors suggest there is a loose positive correlation between maximum likelihood
strength and total points, which is undoubtedly true. However, the x-axis on Figure 2 itself has been
distorted, which makes the trend appear more linear than it really is. I’d prefer to see the x-axis
undistorted, unless the authors are explicitly trying to make a point about the trend being log-linear,
in which case I’d like to see this briefly discussed.
Page 7: The authors suggest we may reject the hypothesis that the strength of the entity exceeds
about 0.025. Does this assertation come with a supporting p-value? It is unclear from Figure 4 how
this conclusion is reached.

### 2022-09-25 inst/surfing_jsa.tex
fixes #168
fixes #169

Table~\ref{rawresults} shows the first few and last few entries in the
dataset we use.  The first line shows that, at one of the heats in
WCT01 (Coolangatta, QLD), Colapinto came first, Bailey second, and
Wright came third: we write
$\mbox{Colapinto}\succ\mbox{Bailey}\succ\mbox{Wright}$.  The last line
shows that, at WCT11 (Banzai Pipeline), Ferreira came first and Medina
second: $\mbox{Ferreira}\succ\mbox{Medina}$.  We can convert this
dataset into a Plackett-Luce likelihood function but first have to
remove the wildcards and also player Vries whose maximum likelihood
strength is zero.  For the first line we would have Plackett-Luce
likelihood function as

>>>>

Table~\ref{rawresults} shows the first few and last few entries in the
dataset we use, drawn from 2019 WSL.  The first line shows that, at
one of the heats in WCT01 (Coolangatta, QLD), Colapinto came first,
Bailey second, and Wright came third: we write
$\mbox{Colapinto}\succ\mbox{Bailey}\succ\mbox{Wright}$.  The last line
shows that, at WCT11 (Banzai Pipeline), Ferreira came first and Medina
second: $\mbox{Ferreira}\succ\mbox{Medina}$.  We can convert this
dataset into a Plackett-Luce likelihood function but first have to
remove the wildcards whose strength is typically very low.  We also
remove De Vries who, while not a wildcard, competed only twice in 2019
and came last each time, thus having zero maximum likelihood strength.
For the first line we would have Plackett-Luce likelihood function as
